### 2023-02-17 main.tex
kk

\begin{equation}
	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{a2l}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}\label{a2lm1}
	\begin{split}
		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
		&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
	\end{split}
\end{equation}

>>>>

\begin{equation}
	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{a2l}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}\label{a2lm1}
	\begin{split}
		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
	\end{split}
\end{equation}
